HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
Typo

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence. We 
%HUME only requires semantically annotating the source sentence,
thus avoiding the semantic annotation of machine-generated text. 
This allows the re-use of the source semantic annotation for measuring the quality
of different translations of the same source sentence.
By basing the measure on a direct comparison
of the source and translation we avoid the difficulties created by using
reference translations, albeit at the cost of requiring the
evaluator to be proficient in both the source and target languages.
%An elaborate comparison of HUME and HMEANT is given in \secref{sec:hmeant_comp}.

>>>>

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence. We 
%HUME only requires semantically annotating the source sentence,
are thus avoiding the semantic annotation of machine-generated text. 
This allows the re-use of the source semantic annotation for measuring the quality
of different translations of the same source sentence.
%By basing the measure on a direct comparison
%of the source and translation we avoid the difficulties created by using
We also avoid creating and relying on possibly suboptimal
reference translations, albeit at the cost of requiring the
evaluator to be proficient in both the source and target languages.
%An elaborate comparison of HUME and HMEANT is given in \secref{sec:hmeant_comp}.
